---
title: ""
author: ""
date: ""
output: 
  pdf_document:
     keep_tex: yes
     includes:
      in_header: header.tex
---
<!-- ************************************************************************************************--> 
<!-- **********************************BEGIN APPENDICES**********************************************--> 
<!-- ************************************************************************************************--> 
\FloatBarrier
\newpage

<!-- ************************************DATA FILE(S)************************************************--> 
#Appendix A. SS data file {-}
\renewcommand{\thepage}{A-\arabic{page}}
\setcounter{page}{1}

```{r, echo=FALSE, eval=TRUE,results='markup', comment=NA}
mod1_data = writeLines(readLines('./SS/linebreak_files/mod1_data.ss'))
```

\newpage

<!-- **********************************CONTROL FILE(S)***********************************************-->
#Appendix B. SS control file{-}
\renewcommand{\thepage}{B-\arabic{page}}
\setcounter{page}{1}

```{r, echo=FALSE, eval=TRUE,results='markup', comment=NA}
mod1_control = writeLines(readLines('./SS/linebreak_files/mod1_control.ss'))
```

\newpage

<!-- *********************************STARTER FILE(S)*************************************************-->
#Appendix C. SS starter file{-}
\renewcommand{\thepage}{C-\arabic{page}}
\setcounter{page}{1}

```{r, echo=FALSE, eval=TRUE,results='markup', comment=NA}
mod1_starter = writeLines(readLines('./SS/linebreak_files/mod1_starter.ss'))
```
\newpage

<!-- ********************************FORECAST FILE(S)**************************************************-->
#Appendix D. SS forecast file{-}
\renewcommand{\thepage}{D-\arabic{page}}
\setcounter{page}{1}

```{r, echo=FALSE, eval=TRUE,results='markup', comment=NA}
mod1_forecast = writeLines(readLines('./SS/linebreak_files/mod1_forecast.ss'))
```
\newpage

<!--********************ADD ADDITIONAL APPENDICES AS NEEDED********************************************-->
<!--********************cHANGE APPENDIX TITLE AND THE APPENDIX LETTER**********************************-->
#Appendix E. Appendix Title{-}
\label{sec:AppendixE}
\renewcommand{\thepage}{E-\arabic{page}}
\renewcommand{\thefigure}{E\arabic{figure}}
\renewcommand{\thetable}{E\arabic{table}}
\setcounter{page}{1}
\setcounter{figure}{0}
\setcounter{table}{0}

Add Appendix text, tables and figuers here.